
Tarn walked slowly back towards his quarters, trying to comprehend what had just happened.  He'd been asked by the king to go on a journey: days of road travel, to a Human town.  Tarn had never strayed far from the mountain, and had slept every night of his life within Kobarthrond.  He shuddered.

Could he abandon his guard responsibilties to go on this mission?  There was a sense of duty drilled into him through years of training and following orders.  But this was an order from King Athzad himself!  Surely he was just making excuses at this point.  Finding himself suddenly desiring counsel, he turned and, instead of going home, decided to visit a close friend.  Tarn followed the corridor until he came to the door with the desired inscription:

\dwarvenInscription{orvi kogugim}

\emph{Orvi, son of Kog}.  A metalworker, Orvi had been Tarn's friend since childhood.  Tarn knocked on the door.  About a minute later, the door opened.

``Tarn?''  Orvi rubbed his eyes.  He was wearing his dressing gown and holding a lantern.

``Hello my friend.  I'm sorry for calling so late, but something's troubling me.''

``Of course, come in!''  Orvi stepped aside, allowing Tarn to enter the apartment.  He turned up the lantern and hung it on the wall to illuminate the sitting room.

Like Tarn's, Orvi's home was decorated with a number of crafted goods, but here most of them had been made by Orvi himself.  Hanging on the far wall was a large knife, its shiny steel blade etched with words---probably merely ceremonial or decorative; it didn't look to Tarn like it had ever been used.  On Orvi's table were a fruitbowl and water jug, made from bronze with elaborate patterns engraved on them and delicate moulded shapes dancing around the rims.   Sitting on a shelf above the fireplace was a row of small ingots, perfectly shaped and polished to a mirror finish, each of a different metal.  Other shelves and furniture proudly displayed various machinery, figures, and coins, all metal and all beautiful.  Upon seeing these fine creations---and, almost as a reflex, thinking about the work and care that went into them---Tarn quickly calmed down, feeling at peace.

He sat at the table, and looked first at the water jug and then at Orvi.  ``There's a problem with the city's water supply.''  After reflecting for a moment, Tarn added, ''the king asked me not to spread it widely and create a panic, so please keep this to yourself.''

Orvi nodded.  ``What kind of problem? I went down to the well just this morning.  I use water every day to quench my pieces of work, and I haven't noticed any issues.''

``The wells are still operating, and open for industrial uses.  We just can't use them to get drinking water.  Some sort of poison, apparently."  Tarn sighed.  ``I disagreed with the king's planned course of action, and in exchange he strongarmed me into journeying to Silverdale.''

``What \emph{was} the king's planned course, that you found it so disagreeable?'' Orvi asked.

``One team is searching the mines for new wells or underground streams.  Another is starting to haul water in from the river.  The city is also buying water from Silverdale---my friend Lawrence brought some in just this week.''

``And you don't think those will work?''

``Not in the long term, no,'' Tarn answered.  ''I think the search will fail, and the other two approaches are too expensive or impractical.''

Orvi nodded slowly.  The silence made Tarn feel uncomfortable; defensive.  ``You disagree?''

``I think they're worth trying.  After all, we need to do something.  What are you supposed to do in Silverdale?"

``The king wants me to ask around, and see if I can find any advanced technology or medicine that can help us.  It was my suggestion, actually; all he did was volunteer me for the job.''

Orvi knew how close Tarn was with his Human friend Lawrence, and that he had a soft spot for Men in general.  ``You seem optimistic about it.''

``Less pessimistic than about the other ideas, I suppose.  But I still feel uncomfortable about the whole thing."

``About your chances?''

``No,'' Tarn answered, ``about leaving for Silverdale.''

``Ahh,'' sighed Orvi sympathetically.  ``It's natural to want to stay here, underground; straying outside is asking for trouble.  So don't discount your gut feeling about this journey.''

``But don't you think it's worth trying, even if I \emph{am} scared, for the sake of the city?''

Orvi thought for a moment, and then spoke slowly, deliberately.  ``If you want my honest answer, I think you're being too idealistic about the Men.  They don't have the answer for everything.  I don't think you're going to find much out there.  And in the mean time, it sounds like the king has things under control.''

His friend's confidence gave Tarn some relief.  He thanked Orvi for his time, wished him well, and left.  It had been a long evening of merry reunions and sobering discussion, and eventually Tarn managed to get to sleep.

The next day Tarn was again on duty, posted at one of the city's banks.  At least by working he was able to contribute---who knows how much time he could have wasted by travelling, and with the possibility of no benefit!

But it was hard to focus on his work.  The water problem still gnawed at him, pulling at his attention constantly.  \emph{How long can the city survive without drinking water?  How long could the citizens survive off beer, wine, and whatever dribbles of water could be imported?  How long could the economy bear those endless imports?}  There was no guarantee that a new water source could be found.  And if one was, who was to say that it wouldn't share the same taint as the city's existing wells?  He could remain here, living his life, patrolling, and ignoring the problem \ldots{} but what good was it to guard a city when that city was dying?

Could he in good conscience stand by while this crisis unfolded?  He was nobody special; not an alchemist or a plumber, with expertise in the problem.  And certainly not an adventurer or scholar, with the ability to find the solution. But unlike most others, \emph{he} knew about the problem; \emph{he} believed in the outside chance of a solution being out there; and what's more, \emph{he alone} had been ordered by his king to go and do this.

All three of these points resonated, humming in Tarn's mind like harpstrings.  If he didn't go, who else would?  Who else would believe in the possibility of an answer, and thus be sincerely driven to find it?  Where would a more cynical Dwarf draw the line and say `sorry Your Majesty, but you were right---there's nothing out there that can help us'?

No \ldots{} it had to be him.  But that was easier said than done; Tarn had never left the shadow of the mountain.  He didn't know where to go, or whom to meet, or what to ask, or even what he should pack.  So he drew a line around this adventure: it would be small; controlled.  He \emph{would} travel to Silverdale, but only to its library.  There, he would ask if there was some obvious solution---that is, obvious to Men but not to the Dwarves of Kobarthrond.  Then, whatever the answer, he would come home and report his findings to the king.

Having a plan made Tarn more relaxed: it was under control.  He'd go, then come back.

\chapter{The Mountain Road}

After his shift, Tarn went to visit Lawrence at the inn.  The trader was still in Kobarthrond, and Tarn found him at the inn's stables, loading his cart with crates.

``Lawrence!'' he called out.  ``Are you leaving the mountain?''

``Tomorrow at sunrise, yes.  Come to say goodbye?''

``As a matter of fact, I came to ask if I could accompany you back to Silverdale.''

Lawrence was taken aback.  ``Uhh, sure!  I must say, I'm surprised---in all our years of friendship I've never known you to be the traveling type.''

``I'm not.  Last night after our parting, I spoke with the king.  There \emph{is} a problem with the water supply after all.  This is confidential, but''---he lowered his voice---``the city's wells are poisoned, and a number of persons have already become sick in the stomach.  He asked me to travel to Silverdale, to find out whether the Men know of a technology or medicine that might help.''

``I see,'' said Lawrence slowly.  Then, his regular brightness returning as if he had simply shaken off those heavy thoughts, ``well that does indeed sound like a worthy quest.  And a good excuse to begin your traveling career!''

``Career?  Please; I'll be satisfied for life with this one short trip.''

Lawrence continued.  ``In any case, of course I'd be happy for you to come with me!  You'll need to a few days' supply of food and wat---well, drink.  And I don't suppose you own a bed roll?''

``No, I don't,'' Tarn replied apologetically.

``Not to worry; once we leave view of the gates, the grass gets quite thick and soft by the side of the road.  Just be sure to pack a good, warm cloak.  Now, you'd best be off and get some sleep.  Can you meet me here, at six o'clock tomorrow morning?''

``I can certainly do that.  Good night my friend.  And thank you.''

``See you tomorrow!''

Tarn stopped by the headquarters of the city guard, and explained the situation to his captain.  This was by order of the king, and so there was little trouble.  He then went back to his quarters, to pack for the journey.

In addition to his cloak, he would bring his hammer, shield, and helmet.  He didn't expect any trouble along the road, but they made him feel comfortable and able to protect himself.  He packed fruit, mushrooms and smoked meats to last a few days, and a small cask of beer.  He filled up his water skin with the last dregs from the water barrel in his apartment.  That and the beer would need to suffice for a day or so, until they came to the river.

Finally, he filled a small purse with coins of gold and silver, the ultimate lubricant for clashing cultures.  Tarn could speak a little Human; the Dwarves of Kobarthrond learned as children, as the country around their mountain was mostly occupied by Men, and the nearest large city was a Human city.  But he was by no means fluent, and the Men that might be able to help him may not speak any Dwarven, so he may need all the help that a few silver coins could provide.  In the worst case he could hire a translator, even Lawrence, to facilitate things.

Feeling that everything was ready, Tarn went to bed and closed his eyes.  Visions of the journey to come filled his head.  He saw the open road and the wide green plains and felt powerless, that this was a world made by the creators, not dwarf-made, and he would need to adapt to it, react to it, with no agency.  He saw the endless blue sky and felt utterly vulnerable, that something terrible could approach from any direction and he would be defenseless.  He drifted to sleep with troubled dreams.

Tarn awoke early, heart pounding and skin covered with sweat.  \emph{You are going to do this}, he told himself, \emph{and you will need to just handle it}.  After cooling down, he got dressed, gathered his things, and stepped through the door.

When he reached the stables, Lawrence was already awake, hooking his cart up to his ox and making the final adjustments to his load.  It always amazed Tarn to see the way that humans were able to use animals in this way, taming and breaking wild beasts to become useful labourers.  As far as he was concerned, animals were there to be hunted for food, defended against, or avoided.  Lawrence saw him and waved.

``Good morning!  Did you sleep well?''

``Just the thought of leaving home gave me nightmares,'' Tarn admitted, ``but I'm ready.''

``Good to hear.  Come on over and I'll pack your gear.''

Tarn approached, and Lawrence took his pack, shield and helmet and tucked them between two crates.  ``I'd like to hold onto this, if you don't mind'', Tarn said, holding up his hammer.

``Fine by me, but I'm confident you won't need it.''

Lawrence then put the cask of beer towards the front of the cart, high up on top of some other cargo.  ``For when we get thirsty!'' he explained.

``Is there time for me to have some breakfast?'' Tarn asked.

``Of course!  The food is quite good at the inn here; let's both have something.''  Lawrence secured his ox to a post, and they went inside.

Tarn took special care to enjoy this meal, as it would be his last comfortable one for at least a week.  On the road they'd be eating cold rations or hunted critters, and once he reached Silverdale \ldots{} he had no idea what he'd be eating.  So he made the most of it: roast mutton, pork sausages, eggs, cave mushrooms, and two mugs of stout beer.

``How long will it take to get there?'' Tarn asked between bites.

``It's about fifty miles from Orehome to Silverdale, so I expect we'll be on the road three days, three nights.  Today's Tuesday, so we should reach the gates before lunchtime on Friday.''

It may have been short as far as journeys go, but Tarn wasn't thrilled at the prospect of sleeping out in the open for three nights.  \emph{Ah well}, he though, \emph{this is what I signed up for I suppose}.

They finished their breakfast, paid the innkeeper, and walked back to the ox cart.
There was no way that Tarn could get onto the cart's seat by himself---it was designed for Men, and Dwarves were quite a bit shorter and stouter.  Lawrence took a crate from the back of and set it down as a step, and Tarn was able to climb in.  Lawrence replaced the crate, untied the ox, climbed aboard on the other side of the seat, and they began moving.

As the cart was pulled through the entrance hall towards the gate, a few Dwarves stared at Tarn.  It wasn't terribly odd for a dwarf to leave Kobarthrond, but Tarn was clearly not a hunter searching for food or a craftsman selling his wares.  Guards remain in and around the mountain, and certainly don't belong on trade carts for long journeys.

Tarn glanced up at the inscription on the wall, imploring him to \emph{be true} and \emph{shine}.  All he could think was that he was a Dwarf, a guard, and not an adventurer, and that if he were being true to himself he'd hop right off that cart and get back to work.  

But regardless of Tarn's self-doubt, and of the other Dwarves echoing it with their suspicious looks, he and Lawrence made it out the gate and into the bright day.

It was a pleasant spring morning, and the air was full with the sounds of birds singing and bugs chirping.  The cacophony was overwhelming for Tarn, who never spent enough time outside to get used to it.  He was accustomed to caves: the calm silence of solid rock in every direction, or the muffled rumblings of industry elsewhere in the mountain.  With every buzzing sound he heard near his head, he swore he could feel its perpetrator crawling on his skin.  Likewise, the fresh air was \emph{too} fresh: pollen and grass and animal smells permeated the breeze, making Tarn long for the stale, still, steady air of Kobarthrond.  His senses were overwhelmed: he couldn't smell or feel or hear a thing over the relentlessly \emph{alive} nature, and his eyes were still blinded by the sun.  He knew from experience that it would all subside eventually, but until then he was paralysed.

Gradually Tarn got his senses back.  He heard Lawrence happily talking to himself about how to pick a good spot to camp for the night and what kinds of animals they could expect to hunt along the road.  Although he had recovered from the initial sensual onslaught, Tarn still felt and heard the bumping and shaking of the cart rolling along the road.

``Will the road be this rough the whole way?'' he asked.

``Trust me, it's much better than the grass or the dirt'' came Lawrence's reply.

The road was built from paved stones, long ago by Men.  Silverdale had been settled in part because of its proximity to the Kobarthrond, with the intention always being to trade with the Dwarves.  Humans seemed by their very nature to be suited to this kind of endeavour: they longed for the frontier, for new lands to explore and conquer, and to string together with trade and diplomacy and religion.  In fact, it didn't take long for the original settlers of Silverdale to send a diplomat into the mountain with gifts of leather and chickens.  Eventually, the town realised that water trade would be impractical through the treacherous Riverwood, and so they instead built the road.  Much straighter than the river, its sole purpose was connecting the Men's town to the Dwarves' mountain city.  Even the road connecting it to Westport, the large human city on the other side of the mountain range, was only constructed much later.

Smoother than the grass it may have been, but that didn't make it any less noisy.  Even the crates in the cart were jumping around every now and then, as a wheel hit a loose rock or a particularly tall paver.

``Mind if I ask what your cargo is?''

``Not at all, if you don't mind cracking open that cask!'' came Lawrence's jovial reply.

As Tarn opened up the cask of beer, Lawrence continued.  ``I'm carrying a few things.  The bulk of it is steel armour, mostly helmets and boots.  Dwarf-made armour is always a hit in the markets.  We've also got a big crate of machine parts, springs and cogs and such.  The engineering shops in Silverdale have a constant need of that stuff---Light knows what they do with it.

``Most importantly, there's a chest of silver ingots.  A group of metallurgists gave me a few gold bars when I left, so that I could sell them to the Dwarves for silver.  One gold ingot is worth quite a number of silver, so maybe they needed something a bit more suited to small trades, at a guess.  All I know is that Orehome has a near-endless supply of silver, and that she's always happy to get her hands on some gold in order to make beautiful things out of it.  I trust \emph{you} not to try to rob me, but please also be careful not to share the information with anyone else.''

``You have my word, '' Tarn said as he handed Lawrence a mug of beer.  ``Cheers!''

``Cheers, friend!''  They hit their mugs together and began to drink.

After his mug was empty, Lawrence continued speaking.  ``On the topic of cargo, I'm a bit surprised about what you said last night.  If the city really has no potable water, I really don't think the eight barrels I delivered will last very long.''

``I'm quite sure you're not the only merchant bringing in water,'' Tarn answered.  ``Besides, King Athzad is also looking for new sources within the mountain, and for ways to fetch our own water from the river outside.  Trade isn't the only solution.''

``\ldots{} and he's also sent a guard off to consult with the Humans!'' laughed Lawrence.

``Well, it was I who suggested that somebody visit Silverdale,'' Tarn said.  ``The king simply responded that it should be I who go.  I don't think he believes that I'll find anything.''

``Even if it doesn't work out, at least you'll end up with a story to tell your grandchildren,'' Lawrence offered, hopefully.

``If it doesn't work out,'' Tarn replied sombrely, ``then nobody in the city may \emph{have} any grandchildren.''

``You really know how to darken the mood, don't you?''  Tarn opened his mouth, but Lawrence continued. ``It's no good being dour and depressed while on the road.  Breathe in the freedom, the adventure!''  He then began to sing:

\begin{verse}\poem{The Merchant}
The merchant is free! With his cart and his load\\
any country he fancies can be his abode.\\
\hspace{2em}He can go where he will\\
\hspace{2em}to lands virgin and still,\\
just as long as that wilderness features a road!

The merchant is clever!  A mind to behold,\\
he must choose the best goods to be carried and sold,\\
\hspace{2em}with the costliest price\\
\hspace{2em}for the tiniest slice,\\
'til his axles collapse from his cart full of gold!

The merchant's adventurous!  Seeing lands wide,\\
passing wondrous new sights precious few men have spied.\\
\hspace{2em}With delight he's instilled\\
\hspace{2em}as his vista is filled\\
yet again with the shape of his horse's backside!

The merchant is cunning!  He endlessly plots\\
where to buy something cheap; where to sell it for lots.\\
\hspace{2em}From the farm he takes furs\\
\hspace{2em}to the town's connoisseurs,\\
then it rains on the road and the merchandise rots!

The merchant is trusted!  A citizen rare\\
on whom all can depend to be even and fair,\\
\hspace{2em}with naught cheating for gain\\
\hspace{2em}and naught cause to complain,\\
and to tariff and customs men, naught to declare!

The merchant is loyal!  To one friend, of course---\\
for his partner's his ox, and they'll never divorce.\\
\hspace{2em}The man keeps it in health\\
\hspace{2em}and they build up their wealth\\
until soon he has money enough for a horse!
\end{verse}

That did the trick, as far as Lawrence was concerned: Tarn seemed in a lighter mood.  They went on for the rest of the day, and when the sun started speeding towards the pink clouds near the horizon, Lawrence stopped the cart so that they could set up camp.  They caught some rabbits for dinner, shared another beer, and lay down to sleep.

Tarn found himself wrapped in his cloak and lying on the grass.  Above him was nothing but the stars in the sky.  Maybe this kind of thing appealed to Lawrence, but Tarn couldn't stand it, those same thoughts flooding his head as on the previous night.  The oppressive openness of the sky was too much to bear.  He got up, wandered over to the cart, and lay beneath it.  The world was still alien to him, but at least now there was a roof protecting him from the void, keeping his breath close, and giving him something to reach out and touch.  Tarn slept.

The remainder of the journey was uneventful, though Tarn found it rather more more onerous than it was.  He was glad when on the Friday morning, as predicted, the Human town of Silverdale appeared on the horizon.