Tarn returned the sword yet again to his belt, and carefully stowed the piece of metal in a small pouch.  The realisation that it really could save his city had softened the blow of its being damaged, and he now took care to preserve every piece of the metal that he could.

\chapter{\mothzam\ \driktur}

``That guard came out of here,'' Bes said, pointing down a fork.  ``My guess is that if \mothzam\ Redbeard is in these tunnels, we'll find him this way.''

The others had no reason to disagree, so they followed Bes and her light.  There were no more forks in the path, and before long they came to yet another wooden door in a rough stone doorway.  They could see a glow around the door here, too, but this time it was a bright blue in colour.

``This might be \mothzam,'' whispered Bes.  ``Make sure you're ready.''

Tarn drew his sword and hammer.  Peter summoned a holy shield around the three of them.  They exchanged a nod, and Tarn opened the door.

This room was less rough than the one containing the elemental.  The floor was flattened, the walls and ceiling smoothed.  The corners and edges of the room were encrusted with ice.  Around the walls, Dwarven glyphs were carved into the stone and glowed faintly with that same unearthly blue that could be seen from outside.

A dwarf stood facing the wall to the left, wearing a black hooded robe.  His left hand was outstretched to touch the blue glyphs, and his right held a wooden staff.  At the top of the staff was what looked like a small brazier, and it held a glass orb containing a glowing blue liquid.  The dwarf continued to focus on the glyphs under his hand, seemingly ignoring the trespassers.  His eyes likewise seemed to glow as they reflected the blue light, and each of his breaths hung like a cloud in the cold air before dissipating.  Falling from his face was a long beard: untrimmed, disheveled, and bright red.

``\mothzam\ \driktur,'' Tarn affirmed.

The hooded dwarf opened his mouth to speak, but his body and eyes remained fixated on the wall in front of him.
``Why have you intruded here?'' he asked in a distracted, unemotional voice.

``We found the elemental.  Imprisoned, neglected, tortured by years of decay and stagnation.  How could any cause justify that level of cruelty?''  The two were speaking Dwarven to each other, and all that Peter and Bes could do was to pay attention to the tone each of them used when speaking, and remain ready for combat should it come to that.

``The creature is mine, and I will do with him as I wish.  If I prefer him to be encumbered by filth, then so will it be.''

Tarn stepped forward, and held up \kildir.  ``I have purified him.''

\mothzam\ turned his head towards them and looked at the sword; he saw the truth of Tarn's words in the shining metal.  His face hardened as he slowly turned the rest of his body.  He withdrew his hand from the glyphs in the wall, to instead hold his staff with both hands.  It began to glow blue along its entire length.  \mothzam\ pointed the staff at Tarn menacingly.

``Do you know the history of that blade?'' he asked Tarn, now sounding angry.

``I know that it came from a floating city which is now sunk.  I know it was used to purify their water, thousands of years ago.''

``And what do you think of its quality?''

Tarn was honest.  ``It is a beautiful artefact, made with unparalleled care and craftsmanship.  I deeply regret the damage it has taken.''

``It is a relic of \valdunmir, the lost dwarven city.  It is but one example of the wondrous works that came from that city, but you can be sure that there were entire industries, over decades or centuries, producing goods just as impressive as that sword.  An entire culture, lost to the seas.''

This produced in Tarn a deep sense of longing; nostalgia for a culture he didn't remember or know.  Desire for the treasures of which \mothzam\ had spoken.

``And not just small handcrafts,'' he continued. ``The city was itself a marvel.  Constructed of iron, yet floating above the seas.  Sprawling gardens and mighty towers.  Engineering and construction unparalleled even now by Dwarves or Men.''

``None of this justifies years of torture, and a dead city cannot be resurrected.''

``It can!'' snapped \mothzam.  ``The machines and platforms sit idle on the bottom of the sea, ready to be restored.  The materials and goods still fill the flooded storehouses.  The people are drowned, but their culture and knowledge still live in the libraries and records, waiting to be drawn up from the waves.

``And I had a way to do it.  The frost elemental I captured, whom you so kindly gave a bath, has power over the seas.  He and his kin could have reversed the calamity that befell \valdunmir, and brought it back to the surface.  All he needed was the right motivation.  And he was close to his breaking point; I know it!  Now you have ruined those years of work.''

``He's free of that now.  Just let him go, if he is no longer any good to you,'' pleaded Tarn.

``Nonsense.  I can find other ways to encourage him.  But you, on the other hand \ldots\ I can see in the way you hold that sword, the way you listened to my words: you understand the value of the prize I describe.''  Tarn said nothing.

``Join me.  Join my team, and help me to restore the glory that was lost; the glory of our people!''

Tarn answered in the Human language in order to warn the others what was coming.  ``You have gone mad with greed, with dreams that can never be fulfilled.  I will not join you.''

Before anybody could react, \mothzam\ thrust his staff towards Peter.  A beam of blue light shot out of it, and an explosion of steam and white powder erupted where it hit him.  Peter ceased all movement, as he was now encased in a massive lump of ice.

Tarn bellowed, and begain sprinting towards the other dwarf.  He threw \kildir\ to the floor and reached for his hammer and shield.  At the same time, Bes snapped into action and began conjuring a fireball with her staff.  Before she could release it though, \mothzam\ summoned hundreds of pointed shards of ice, which flew from his staff to hit Bes in the chest.  She cried out in shock, and collaped to the ground, punctured, bloody, and writhing in pain.

Tarn got close enough for a strike, and pulled his hammer back.  He swung it just as \mothzam\ turned towards him, and staff and hammer met.  The force knocked both of them off balance.  With this powerful wizard as an opponent, and his two allies out of the fight, Tarn knew that he was outmatched.  If he were to survive, this battle must not be allowed to stretch on.  It needed to end now.

He dropped his shield, to grasp his hammer with both hands.  He leapt at \mothzam, whose mouth was muttering something and whose staff was now raised, with blue points of light being sucked into the orb as if something were growing there.  Falling now upon his opponent, Tarn swung the hammer hard and fast, strengthened by bloodlust, by revenge for his friends, and by the sheer will to survive the next few seconds.  A ball of frost appeared in the air from the staff, and flew straight towards Tarn with sudden speed like an arrow just released.  In the same instant that the frost ball hit Tarn in the stomach, Tarn's hammer met \mothzam's robed chest with the horrible sound of metal breaking bones.  Tarn fell to the ground, winded and cold, but uninjured.

Bes, lying on the floor still clutching her staff, struggled to turn and look at Peter.  She winced in pain as she tried to mutter a spell, her voice wavering between anguished moans and the scarcely audible syllables of her incantation.

A yellow flame then appeared, dancing on the end of her staff, while a corresponding glow began to fill the block of ice surrounding Peter.  As the ice became brighter and warmer in colour, it rapidly melted, until soon Peter had collapsed to the floor in a large puddle of water.  He slowly got up, shivering, and looking around.  The two dwarves were lying together on the floor.  Tarn seemeed to be recovering, but \mothzam\ was mortally wounded, his breathing laboured and a puddle of red growing on the stone floor around his beard.  Peter then turned to look at the pyromancer.  She too was on the floor, having suffered countless savage wounds from the ice shards.  Her hand held her staff, now dark and cold.  She was no longer breathing.  Peter hurried to her side, fell to his knees, and wept.

Tarn inspected \mothzam.  The dwarf's staff was out of his hand now, the blue glow gone from all but the orb at its top.  \mothzam\ inhaled loudly, painfully, and spoke to Tarn.

``I am finished \ldots\ but you can still \ldots\ restore \valdunmir\ \ldots\ This is bigger than me \ldots\ bigger than you \ldots\ for the glory of our people \ldots use the elemental.''

Tarn merely stared, as \mothzam\ \driktur\ breathed his last.

``Bes has died,'' Peter said, as Tarn walked towards them sadly.  ``Did she know that \mothzam\ was defeated?''

``I'm sure of it,'' Tarn replied.  ``I mourn the passing of our friend.  But what glory, for one so deeply aggrieved by an enemy, to fall in a victorious fight against him!''

``Glorious indeed.  Though it is always a great tragedy when an immortal elf dies.  She ended her life as a good person; she fought not for revenge, but to thwart an unnatural scheme, and out of compassion for the suffering of that elemental.  I believe that she will be rewarded by the Light for her promotion of the good.''  Tarn had neither the knowledge nor the inclination to disagree.

The elf had few possessions.  They found a purse full of coins, and a small codex containing knowledge of pyromancy.  These Peter took, with the intention of returning them to her people.

``Shall we bury her outside?'' asked Tarn.

``I don't think we can do that without being seen by the villagers.  The only respectful option we have is to burn her remains.''

``Aye.  Do you know how to use that?'' Tarn asked, pointing to Bes's fire staff.

``No, but the Light can provide cleansing fire when needed.''

They lay the elf's body straight in the middle of the room, with her staff in her hands.  Peter then prayed by her side, until the body was consumed by a large fire.

``It will burn until her body is no more,'' he said to Tarn.

% Funeral song here, even if short?

Their solemn duty done, they turned to \mothzam\ \driktur.  The only possession he carried was the orb-topped staff.  Tarn picked it up and examined it.  He reached out to the orb, pulled it out of its enclosure, and found that it was actually a round bottle.

``The elemental's essence?'' he pondered.

``It must be,'' answered Peter.

Tarn stuffed the vial into his belt, and turned to leave the room.  Hanging on the wall by the doorway was a shield; clearly Dwarven made, but it was very old.  On the inside was an inscription:

\dwarvenInscription{ar im skamzold\\*rovkimugin}

\emph{Prince Skamzold, son of Rovkim}.  Perhaps the shield belonged to this Prince Skamzold? On its centre was an engraving of the side view of a city, with countless towers rising from a flat base.  Beneath the city were the images of waves.  Tarn supposed that this was an image of \valdunmir, and he decided to take the shield with him.

Peter picked up the frost staff, and the two walked through the door, with Bes's body respectfully burning in the room behind them while \mothzam's lay crumpled in a disgraced heap on the floor.
