When the sun was setting and half of the sky was already dark, they reached the banks of Silverdale.  It had been many hours, and they had gone past countless settlements before reaching this one.

``Thank you once again,'' said Tarn.  ``Your swiftness has saved me an enormous amount of time and trouble in returning here.''

``Again, you have done me a much greater service; I owe you my freedom and my health.  From this moment onwards I want you to consider yourself a friend of the Frost Elementals.  Legends of you, and your deeds, and your magical sword will spread throughout the waterways and frosts of the world.''  Tarn was speechless.  ``But now I must leave you, and return to my kin.  It has been too long since I have seen them.  Farewell, Tarn of Orehome.''

``Farewell, my friend,'' the dwarf said wistfully.  The elemental disappeared into a wave, which returned the way they had come.  Soon the river was flat once more.  Tarn was now alone, for the first time since he was here in Silverdale, all those long days ago.  Once again soaking wet, he walked up the bank into the town.  The people passing him gave odd glances at the armoured dwarf, laden with weapons and shields and dripping water onto the street, but gave him no trouble.  Eventually he reached the library.

Tarn entered the building, and saw Ithur standing behind the desk.  It was an odd sensation; almost as if he had left the library only for a brief moment.  Ithur looked up, and his eyes widened.  ``You have returned!''

``I have.  And I have quite a story to tell you.  But first''---he shuffled around the items in his arms, and produced the scroll and pouch---``these are for you, from Lord \arilor\ of \inarthonor.''

``\inarthonor!  You must have traveled far indeed.''  He opened the pouch, and exclaimed, ``these are seeds, from a number of herbs and flowers that I do not own.  This gift will greatly improve my garden!''  Then he unrolled the scroll.  ``And this is the best gift of all: information.  It is an account, in Lord \arilor's own hand, of your adventure as told to him.  I will study this carefully, and make sure our records are updated and augmented accordingly.''

Tarn was relieved that \arilor\ had done the work of telling most of his story for him.  He didn't relish the idea of reciting it yet again, but more importantly, he was eager to get back home.  Tarn stayed for about an hour, answering questions, clarifying details, and describing landscapes and directions and distances while Ithur took notes and made rough sketches.  Ithur also sketched \kildir\ and the prince's shield.

``I am sorry, but it is late and I must find an inn before my journey home tomorrow.  I hope that what I have given you is enough.''

``It's more than I could have hoped for,'' said Ithur, smiling.  ``Get your well-deserved rest, and hurry home to help your city.''  Tarn left, and found an inn for the night.  He slept soundly and deeply; his most comfortable night in a long while.

In the morning, Tarn went straight for the stable at the city gate---the same place he had met Peter.

``Good morning.  I would like to hire a swift pony to take me to Orehome.''

The proprietor smiled and nodded.  He went into the stable building, and returned soon with a brown pony, saddled and ready.  Tarn thanked him and paid.  After securing his belongings he mounted up, passed through the city gate, and galloped as fast as he could along the mountain road back to \korbarthrond.

It was early afternoon when Tarn arrived at the city gates.  Upon entering the familiar mountain, it felt like his heart grew in his chest from being so full of comfort and familiarity.  He rode the pony to the \korbarthrond branch of the stable, dismounted, picked up all of his items, and walked to his quarters.

Tarn would have loved to spend hours finding the best place for his new shield, and enjoying the comforts of his home and its treasures, but he still had a mission to accomplish.  He quickly took off his armour and dropped everything onto the floor. He picked up \kildir\, the prince's shield, and a purse of gold coins, and left again.  Walking briskly, he followed the hallways through the mountain fortress until he reached the door of his friend Orvi, the metalworker.