\chapter*{Epilogue}
\addcontentsline{toc}{chapter}{Epilogue}

Tarn woke up, and got ready for work.  He dressed in his guard's uniform, and picked up his hammer.  He glanced at the shield hanging on his wall, a prince's ceremonial shield from dwarven antiquity.  Not as strong as his issued shield, and far too beautiful to use in combat.  In any case, it wasn't part of his uniform, so he picked up his issued shield and strapped it to his back.

Below the shield was a small shelf containing the jewelry box, opened to display the ring made from \kildir's metal.  He picked up the ring and slipped it onto his finger.

Tarn left his quarters and headed to the mess hall for breakfast.  Along with his plate of sausages, eggs and cave mushrooms, Tarn had a mug of beer, and then a mug of water.  He drank the water slowly, deliberately, enjoying every sip.  It was the cleanest water Tarn had ever tasted.

As he drank, he looked at his ring.  \valdunmir\ was still at the bottom of the sea, and there it would stay.  The Tholkis wanted to resurrect the city's spirit, its technology and magic.  But where \mothzam\ \driktur\ had lamented the loss of this culture, Tarn instead smiled: \valdunmir's technology \emph{had} been resurrected.  It lives on, now in the heart of \korbarthrond, and by ensuring the health of the dwarves it was keeping this city afloat.

As Tarn began his day's work guarding the fortress, he knew that he would never again feel that urge to restore the sunken city.  He had his own city---just as magical, and just as important---and it was his job to maintain and protect it.